Gaia identifies VFTS682 as the most massive runaway star known to date

### 2018-05-11 VFTS682.tex
trying to recover access without damages

%Selma's comments
\definecolor{Wildstrawberry}{rgb}{1.0, 0.26, 0.64}
\newcommand{\SdM}[1]{{{\color{Sepia}{#1}}}}
%\renewcommand{\SdM}[1]{{{{#1}}}}

@@

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$,
  S.~Justham$^{3,4}$, J.~Vink$^{5}$, F.~R.~Schneider$^6$, A.~de~Koter$^{1}$ \todo{... add coauthors...} }

@@

% %%% change \tablenotetext{a} -> \tablenotetext{1} etc. to omit LaTeX errors
% %%% Karol Kozio? for ShareLaTeX

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{./figures/main_plot}  
  \caption{The red solid arrow indicates the proper motion of VFTS682
    relative to the region, starting from the present day position of
    the star. The semi-transparent arrows indicate the possible
    directions of projected motion within the errors, and are extended
    backwards to illustrate the uncertainty on the origin of the
    star. The blue stars
    are a subset of those we use to define the local rest frame. \todo{load color picture on background}}
  \label{fig:main}
\end{figure}

\section{Discussion}
\label{sec:discussion}

@@

Dynamical ejections due to N-body interactions typically (although, not necessarily) eject the least
massive star among those interacting \todo{ref}. This means that, just
based on the kinematic properties of VFTS682, we would expect several
stars with initial masses larger than $\sim$$150\,M_\odot$ in the
cluster R136.
This is consistent with the detection
of extremely massive stars by \cite{crowther:10} in the core of the
cluster. The projected rotational equatorial velocity of VFTS682
reported by \cite{schneider:18} is $v\sin(i)<200\,\kms$, which is in
line with the average rotation rate of massive stars in the region
\citep[][]{ramirez-agudelo:15}. This suggests that VFTS682 (i) has not
experienced rotationally induced chemically homogeneous evolution
\citep[][]{maeder:00,demink:09,marchant:16}, and (ii) it has not
accreted mass from a binary companion, nor it will, since the multi-epoch
data of the VFTS survey rule out the presence of a companion at
present day. Moreover, the spectral type of VFTS682
\citep[WNh5,][]{bestenlehner:11} is the same as R136a1-a3, i.e.~the
three most massive stars detected in the core of the cluster by
\cite{crowther:10}, with an astonishing similarity in particular with
the spectrum of R136a3. Therefore,
VFTS682 might be an ideal target to constrain the stellar physics of
stars with masses well above $\sim$$100\,M_\odot$: its isolation makes
it an easier target for observations compared to the similar stars
present in the crowded core of R136.

@@

\begin{itemize}
\item is R136 a single young cluster or a merger
\item estimate the influence of the gravitational potential of R136,
  what is its total mass and relaxation time?
\item Make link to dynamical interaction proposed to form BHBH systems.
\end{itemize}

>>>>

%Selma's comments
\definecolor{Wildstrawberry}{rgb}{1.0, 0.26, 0.64}
\newcommand{\SdM}[1]{{{\color{Sepia}{#1}}}}
\renewcommand{\SdM}[1]{{{{#1}}}}

@@

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$,
  S.~Justham$^{3,4}$, J.~Vink$^{5}$, F.~R.~Schneider$^6$,
  J.~Bestenlehner, A.~de~Koter$^{1}$ \todo{... add coauthors...} }

@@

% %%% change \tablenotetext{a} - \tablenotetext{1} etc. to omit LaTeX errors
% %%% Karol Kozio? for ShareLaTeX

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{./figures/main_plot_good}  
  \caption{The red solid arrow indicates the proper motion of VFTS682
    relative to the region, starting from the present day position of
    the star. The semi-transparent arrows indicate the possible
    directions of projected motion within the errors, and are extended
    backwards to illustrate the uncertainty on the origin of the
    star. The blue stars
    are a subset of those we use to define the local rest frame. \todo{load color picture on background}}
  \label{fig:main}
\end{figure}

\section{Discussion}
\label{sec:discussion}
\todo{Selma: Should add caveat that it may be a spurious detection.  That reconfirmation in following epochs is warranted. }

@@

Dynamical ejections due to N-body interactions typically (although, not necessarily) eject the least
massive star among those interacting \todo{ref}. This means that, just
based on the kinematic properties of VFTS682, we would expect several
stars with initial masses larger than $\sim$$150\,M_\odot$ in the
cluster R136.
This is consistent with the detection
of extremely massive stars by \cite{crowther:10} in the core of the
cluster. The projected rotational equatorial
velocity\footnote{However, the determination of the rotational
  velocity for stars showing lines in emission is complicated because
  of the optically thick wind screening the surface of the star, and should be
  considered with caution.} of VFTS682
reported by \cite{schneider:18} is $v\sin(i)<200\,\kms$, which is in
line with the average rotation rate of massive stars in the region
\citep[][]{ramirez-agudelo:15}. This suggests that VFTS682 (i) has not
experienced rotationally induced chemically homogeneous evolution
\citep[][]{maeder:00,demink:09,marchant:16}, and (ii) it has not
accreted mass from a binary companion, nor it will, since the multi-epoch
data of the VFTS survey rule out the presence of a companion at
present day. Moreover, the spectral type of VFTS682
\citep[WNh5,][]{bestenlehner:11} is the same as R136a1-a3, i.e.~the
three most massive stars detected in the core of the cluster by
\cite{crowther:10}, with an astonishing similarity in particular with
the spectrum of R136a3. Therefore,
VFTS682 might be an ideal target to constrain the stellar physics of
stars with masses well above $\sim$$100\,M_\odot$: its isolation makes
it an easier target for observations compared to the similar stars
present in the crowded core of R136.

@@

\begin{itemize}
\item is R136 a single young cluster or a merger
\item estimate the influence of the gravitational potential of R136,
  what is its total mass and relaxation time?
\item Make link to dynamical interaction proposed to form BHBH
  systems.
  \item from Fabian's email (see comment in tex):% One last aspect: I am always wondering what happens to the star/binary that ejected 682. There is a huge linear momentum in this star of ~150 Msun * 60 km/s. Even if the bully was a 300 Msun total object, it would obtain a kick of 30 km/s. Is this enough to eject the bully star? This velocity would already be 100 km/s for a 90 Msun bully (I was thinking of 016 here... 'Cause I do not know what ejected this object either). Of course, if there is a third body, these velocities are no longer correct. The escape velocity from R136 at 0.5pc for a total mass of 10^5 Msun would only be of order 20 km/s... So a 300 Msun bully is at the edge of what is possible and one might need something even more massive or another very massive object will also be ejected. Or am I wrong here? Do the Banerjee and Co simulations say something about this?
\end{itemize}
